Toward theories of deliberated preferences

### 2020-12-09 simple.tex
Some notes about a requirement about the falsification concept, currently not met.

@@

\section{Preferences}
\label{sec:preferences}
\subsection{Representing deliberated preferences}
Let $\allalts$ be a set of alternatives.

@@

The observation protocol goes as follows. Given $i \in I$, $\emptyset ≠ B \subseteq \allalts$ and $\hist \in \allhist$, the individual $i$, after having been presented the arguments in the sequence $\hist$, is asked to choose among a subset of elements from $B$ among which she is indifferent. Define $\emptyset ≠ c^\hist_i(B) \subseteq B$ as the subset that $i$ chooses after exposure to $\hist$.
Define $\hist \ileadsto \prop_{B, \choices}$ iff $c^\hist_i(B) \in \choices$.

>>>>

TODO distinguigh: exists real relation $\leadsto$ suchthat exists observations that show the claim is false VS forall relations $\leadsto$ not in C, exists observations that show the claim is false. If I claim "a is dec for phi", if this is false, it is possible to show it (second case); but if I claim "a is dec for phi AND some argument is decisive for phi'" (or "$\alpha \ileadsto \phi$ and some argument is decisive for phi"), then the first case is satisfied, but not the second one: if indeed $\alpha \ileadsto \phi$ but NO arg dec, it is impossible to observe the falsity of the claim. Note that the first requirement is satisfied by BR but not the second one.

@@

\section{Preferences}
\label{sec:preferences}
\subsection{Representing deliberated preferences}
A normative theory of deliberated choice is a normative theory of DJ using propositions of a certain form and a specific protocol of observation.

Let $\allalts$ be a set of alternatives.

@@

The observation protocol goes as follows. Given $i \in I$, $\emptyset ≠ B \subseteq \allalts$ and $\hist \in \allhist$, the individual $i$, after having been presented the arguments in the sequence $\hist$, is asked to choose a subset of elements from $B$ among which she is indifferent. Define $\emptyset ≠ c^\hist_i(B) \subseteq B$ as the subset that $i$ chooses after exposure to $\hist$.
Define $\hist \ileadsto \prop_{B, \choices}$ iff $c^\hist_i(B) \in \choices$.
